Efficient, Robust and Exact Boolean Operations on N Triangular Mesh Primitives

### 2016-07-31 summary.tex
before delete

Face classification is to evaluate whether a given face $x$ belongs to the final geometry according to the n-primitive Boolean function $\Phi$ :
\begin{equation}
\lambda_\Phi(x) = \Phi(\lambda_1(x), \lambda_2(x), \cdots, \lambda_n(x)).
\end{equation}
The parameter $\lambda_i(x)$ is space indicator with respect to primitive $P_i$. This means to classify a face, one has to know the space indicators with respect to all the primitives (or the whole indicator vector $\vec{\lambda}(x)$ for short). A space indicator has four conditions: completely inside (\emph{in}), completely outside (\emph{out}), on the boundary with consistent normals (\emph{same}) or opposite normals (\emph{oppo}). The rules of Boolean function evaluation by these indicators are described in \cite{douze2015quickcsg}\cite{feito2013fast}.

@@

We recall our definition of Linked Halfedge in section \ref{sec:meshes}, we need to transfer necessary information by IR to tessellation stage for Linked Halfedge construction. For each intersection line segment, we use a five-component vector {\color{red}{$\gamma \colon(T, v_0, v_1, p, C)$}} to describe it. Here, $v_b$ and $v_e$ are the two end points of $\gamma$. Component $f$ is the face where the $\gamma$ lies. Component $C$ is the intersection context, and will be further explained later. Component $p$ is the plane representation of the line where $\gamma$ lies (denoted as $\vec{n}_\gamma$). Normally, line is represented by two planes. However, one of the planes for $\vec{n}_\gamma$ must be $f$'s supporting plane $p^s(f)$, so we just omit it, and use the other plane as the representation for $\vec{n}_\gamma$ .

To illustrate, assume two triangle faces $f_1$ and $f_2$, from primitive $P_1$ and $P_2$, intersect at line segment $\gamma$. Note that there are two versions of $\gamma$ for each of the two faces respectively, denoted as $\gamma(f_1)$ and $\gamma(f_2)$. For $\gamma(f_1)$, $v_b$ and $v_e$ are the two end points of $\gamma$ and $f=f_1$. The representation plane $p$ is $p^s(f_2)$. Note that $p^s(f_2)$ must not be coplanar with $f_1$. The intersection context $C=f_2$ in most cases. It means that, in primitive $P_2$, $\gamma(f_1)$ lies on the face $f_2$. However, sometimes, intersection may lie on the edge, instead of face,  of other primitive. In that case,  the intersection context is an edge, and we discuss such degenerate case in the next section. The situation of $\gamma(f_2)$ is similar we omit the discussion here.

@@

Assume there are two faces $f_1$ and $f_2$ from primitive $P_1$ and $P_2$ respectively. These two faces intersect on line segment $\gamma$, which has two versions of IR $\gamma(f_1)$ and $\gamma(f_2)$ for the two faces respectively. Without loss of generality, we only discuss the configuration of $\gamma(f_1)$, as $\gamma(f_2)$ can be figured out similarly. We classify all degenerate cases into three categories by the dimension of intersection. Each of them is discussed separately in the following.

@@

When intersection line segment lies on an edge (Fig. \ref{fig:twin}). we call it as \emph{edge intersections}. There are generally two kinds of edge intersections. If $\gamma$ lies on the edge of $f_1$ or $f_2$, but inside of the face of the other one, then we called it as edge-face intersections. If $\gamma$ lies on the edges of both $f_1$ and $f_2$, we call it as edge-edge intersections. When there is edge-face intersection, we treat it as the intersection of three faces $f_1$, $f_2$ and $f_1^\star$ (or $f_2^\star$). When there is edge-edge intersection, we treat it as the intersection of four faces $f_1$, $f_2$, $f_1^\star$ and $f_2^\star$. The $f_1^\star$ (or $f_2^\star$), known as \emph{companion face},  is the neighboring face which shares the intersection edge with $f_1$ (or $f_2$). In this way, we avoid repetitive insertion of the same edge intersections, since the companion faces share the same intersection with its neighborhood $f_1$ or $f_2$.

@@

The key observation is that coplanar cases do not create new edges, just like edge intersection in the last section. The difference is that in a non-coplanar case, there is only one edge intersection. In a coplanar, there are at most three intersections. Therefore, we can decompose it into three edge intersections and record each edge intersection independently. However, there is a better way that we do not process them at all. This is because there is companion face, like $T_1^*$, in edge intersection. If $T_1^*$ is not coplanar with $T_2$, then we can solve the intersection between $T_1^*$ and $T_2$ in a 3D way, which is the case in Fig \ref{fig:twin}(c). On the other hand, if $T_1^*$ is coplanar with $T_2$, we instantly know that both sides of shared edge $e(T_1, T_1^*)$ have the same indicator $\lambda_1$, which imply that this intersection is not necessary for tessellation and we can omit it by the principle of concision. In sum-up, we do not need to handle with coplanar intersection cases.

@@

Using plane-based representation, whether two intersections intersects each other is determined by predicate of orientation of plane against a point. For example, we want determine whether $\lambda_1$ and $\lambda_2$ intersects. Using the notation of section \ref{sec:ir}, we perform the test by checking whether $v_0(\lambda_1), v_1(\lambda_1)$ are on two sides of $p(\lambda_2)$ and whether $v_0(\lambda_2), v_1(\lambda_2)$ are on two sides of $p(\lambda_1)$. If yes, $\lambda_1$ and $\lambda_2$ intersects and introduces new intersection vertex $v_{new}$, which is the intersection of $p(\lambda_1), p(\lambda_2)$ and the supporting plane of $T(\lambda_1)$. The new vertex $v_{new}$ should be added into both $\lambda_1$ and $\lambda_2$ as a segment point. Since there may be more than one segment point added into a certain intersection during the whole test, we do not divide the intersection until all intersection pairs are tested.

@@

The space coherence of indicator vectors means neighboring faces could share the same indicator vector, or most components of indicator vectors. For example, given two neighboring faces $t_1$ and $t_2$, indicator vectors $\Lambda(t_1)$ and $\Lambda(t_2)$ would often be the same. Only when there is boundary of some meshes, say $P_k$, on the shared edge $e(t_1, t_2)$ and split $t_1$ and $t_2$ in two sides, the corresponding components $\lambda(t_1, P_k)$ and $\lambda(t_2, P_k)$ can be different. And other components of $\Lambda(t_1)$ and $\Lambda(t_2)$ will remain the same. If we can compute the indicator changes between neighboring faces efficiently, we can start from a single face with a indicator vector as the seed, propagating to all faces with geometry connectivity, reusing indicator vectors according to the spatial coherence and classifying faces very fast.

Fortunately, in the Linked Halfedge, it is straightforward to know whether $\lambda(t_1, P_k)$ and $\lambda(t_2, P_k)$ are different, because it means $e(t_1, t_2)$ will be on the boundary of $P_k$, and there will be corresponding I-reps stored on $e(t_1, t_2)$. In addition, both $\lambda(t_1, P_k)$ and $\lambda(t_2, P_k)$ can be computed efficiently according to the I-reps (details in Section \ref{sec:individual}). We outline our classification method in Algorithm 1.

@@

\textbf{Output: } Classification of each face $f(\Lambda(t_i)), t_i \in \Omega$

\begin{algorithmic}[1]
\State Select a proper seed face $t_s$
\State Compute the first indicator vector $\Lambda(t_s)$
\State \Call{propagate} { $t_s$ , $\Lambda(t_s)$}
\State
\Function{propagate}{ $t_c$ , $\Lambda(t_c)$}
    \State Compute $f(\Lambda(t_c))$
    \For {each neighboring face $t_i^c$}
        \If {there are I-reps $\{\gamma_k\}$ on $e(t_i^c, t_c)$}
            \State Compute $\Lambda(t_i^c)$ using $\Lambda(t_c)$ and $\{\gamma_k\}$
            \State \Call{propagate} { $t_i^c$ , $\Lambda(t_i^c)$}
        \Else
            \State \Call{propagate} { $t_i^c$ , $\Lambda(t_c)$}
        \EndIf
    \EndFor
\EndFunction
\end{algorithmic}
\end{algorithm}

\subsection{Seed Indicator Vector}

@@

However, using point on the boundary instead of an inner one has another problem. Given a face $s$ (may not be triangle) and one of its vertex $v_b^i(s)$, the vertex indicator $\lambda(v_{i}(s), P_k)$ may cause ambiguity to deduce the face indicator $\lambda(s, P_k)$. In {\color{red}{Fig. ?}}, $\lambda(v_b^1(s), P_k) = on$, then $\lambda(s, P_k)$ can be any of the four conditions. We solve this problem by trying other vertices in $s$ for the ambiguous components. If all vertices indicators are $on$ and the ambiguity still cannot be resolved, the current face is not proper for being the seed and select a new one instead.

@@

Feito et. al. \cite{feito2013fast} had noticed that intersection neighborhood can be used for fast classification of faces around that intersection. According to their method, faces adjacent to intersection have neighbors from other primitive(s) that define the position and orientation for each other, by which the indicators are determined. However, Feito et. al. did not give detail description of how to implement an exact and robust classification. Their implementation of using vertex coordinates may have problems for the degenerate cases. Because geometry connectivity is used, local incorrect classification can be spread to the neighborhoods, leading to errors in wide ranges.

{\color{red}{fdafdafdsfafdfadsfa}}

@@

If $I$ lies on edge of primitive $A$,  the intersection context is face pair: $C_{I \mapsto A} = (f_p^A, f_q^A)$. This situation is a little more complex that we cannot decide $i_A$ until we check the orientations of both $f_p^A$ and $f_q^A$. To correctly classify $f$, we first build BSP structure using $f_p^A$ and $f_q^A$ [?], and then determine the space indicator $i_A(v_2)$ by the BSP. As coordinate of $v_2$ and all the planes can be exactly computed, the classification is exact. The indicator of the face $i_A(f)$ should be the same as $i_A (v_2)$. It is because under a BSP structure with only two division planes, any sample point on $f$ except those on $I$ has the same $\lambda_A$ (Fig. ??).

@@

If the CSG tree is large, with tens of, or even hundreds of nodes, computing $\lambda_\Phi(f) = \Phi(\vec{\lambda}(f))$ for every face can be costly. Considering the space coherence of indicator, we use cache techniques --- by storing the evaluation result of $\Phi$ --- to save the computation time.

The most simple cache strategy is final result cache. We know indicator vector $\vec{\lambda}$ will not change if there is no intersection context during spreading. That means the final classification $\lambda_\Phi$ will not change, too. Thus, those faces sharing the same $\lambda$ can be classified as a whole.

Also, we can also do intermediate result cache. It should be noticed that $\Phi(\vec{\lambda}(f))$ can be simplified if some components of $\vec{\lambda}$ is fixed. For example, assume we have a Boolean expression $M_1\cup (M_2\cap M_3-M_4)$. Given the values of two indicators $\lambda_1(x)=out$, $\lambda_2(x)=in$, the expression can be rewritten as $out\cup (in\cap M_3-M_4)$. Using the combination rules we can simplify the expression as $M_3-M_4$. This fact is important because for a large CSG tree, a certain primitive, denoted as $M_x$, often only intersects with a few other primitives $\Theta= \{M_{n_1}, M_{n_2}, \cdots, M_{n_k}\}$. That means all the faces in $M_x$ has the same indicators for the primitives not in $\Theta$. Therefore, we can first determine these fixed indicators and simplify the Boolean function $\Phi$ into a simpler one $\Phi_{M_x}$, and then use $\Phi_{M_x}$ to compute the final indicator for each faces.

@@

\vspace{0.5em}
\textbf{Generate Seed Indicator Vector.} Our method of generating the first indicator vector will fail on extreme conditions when each face in Linked halfedge is coincident with more than one primitive face (e.g., the union of the same mesh). In order to be robust, we use the face barycenter with high-precision coordinates for the point-in-polyhedron test to generate the seed indicator vector after several failures of choosing a proper seed face.

>>>>

Face classification is to evaluate whether a given face $x$ belongs to the final geometry according to the n-primitive Boolean function $f$ :
\begin{equation}
\lambda_f(x) = f(\boldsymbol{\Lambda}(x)) = f(\lambda_1(x), \lambda_2(x), \cdots, \lambda_n(x)).
\end{equation}
The parameter $\lambda_i(x)$ is space indicator with respect to primitive $P_i$. This means to classify a face, one has to know the space indicators with respect to all the primitives (or the whole indicator vector $\boldsymbol{\Lambda}(x)$ for short). A space indicator has four conditions: completely inside (\emph{in}), completely outside (\emph{out}), on the boundary with consistent normals (\emph{same}) or opposite normals (\emph{oppo}). The rules of Boolean function evaluation by these indicators are described in \cite{douze2015quickcsg}\cite{feito2013fast}.

@@

We recall our definition of Linked Halfedge in section \ref{sec:meshes}, we need to transfer necessary information by IR to tessellation stage for Linked Halfedge construction. For each intersection line segment, we use a five-component vector {\color{red}{$\Gamma \colon(t, v_0, v_1, p, C_{P_h \backslash P_i})$}} to describe it. Here, $v_b$ and $v_e$ are the two end points of $\Gamma$. Component $f$ is the face where the $\Gamma$ lies. Component $C$ is the intersection context, and will be further explained later. Component $p$ is the plane representation of the line where $\Gamma$ lies (denoted as $\vec{n}_\Gamma$). Normally, line is represented by two planes. However, one of the planes for $\vec{n}_\Gamma$ must be $f$'s supporting plane $p^s(f)$, so we just omit it, and use the other plane as the representation for $\vec{n}_{\boldsymbol{\Gamma}}$ .

To illustrate, assume two triangle faces $f_1$ and $f_2$, from primitive $P_1$ and $P_2$, intersect at line segment ${\boldsymbol{\Gamma}}$. Note that there are two versions of ${\boldsymbol{\Gamma}}$ for each of the two faces respectively, denoted as ${\boldsymbol{\Gamma}}(f_1)$ and ${\boldsymbol{\Gamma}}(f_2)$. For ${\boldsymbol{\Gamma}}(f_1)$, $v_b$ and $v_e$ are the two end points of ${\boldsymbol{\Gamma}}$ and $f=f_1$. The representation plane $p$ is $p^s(f_2)$. Note that $p^s(f_2)$ must not be coplanar with $f_1$. The intersection context $C=f_2$ in most cases. It means that, in primitive $P_2$, ${\boldsymbol{\Gamma}}(f_1)$ lies on the face $f_2$. However, sometimes, intersection may lie on the edge, instead of face,  of other primitive. In that case,  the intersection context is an edge, and we discuss such degenerate case in the next section. The situation of ${\boldsymbol{\Gamma}}(f_2)$ is similar we omit the discussion here.

@@

Assume there are two faces $f_1$ and $f_2$ from primitive $P_1$ and $P_2$ respectively. These two faces intersect on line segment ${\boldsymbol{\Gamma}}$, which has two versions of IR ${\boldsymbol{\Gamma}}(f_1)$ and ${\boldsymbol{\Gamma}}(f_2)$ for the two faces respectively. Without loss of generality, we only discuss the configuration of ${\boldsymbol{\Gamma}}(f_1)$, as ${\boldsymbol{\Gamma}}(f_2)$ can be figured out similarly. We classify all degenerate cases into three categories by the dimension of intersection. Each of them is discussed separately in the following.

@@

When intersection line segment lies on an edge (Fig. \ref{fig:twin}). we call it as \emph{edge intersections}. There are generally two kinds of edge intersections. If ${\boldsymbol{\Gamma}}$ lies on the edge of $f_1$ or $f_2$, but inside of the face of the other one, then we called it as edge-face intersections. If ${\boldsymbol{\Gamma}}$ lies on the edges of both $f_1$ and $f_2$, we call it as edge-edge intersections. When there is edge-face intersection, we treat it as the intersection of three faces $f_1$, $f_2$ and $f_1^\star$ (or $f_2^\star$). When there is edge-edge intersection, we treat it as the intersection of four faces $f_1$, $f_2$, $f_1^\star$ and $f_2^\star$. The $f_1^\star$ (or $f_2^\star$), known as \emph{companion face},  is the neighboring face which shares the intersection edge with $f_1$ (or $f_2$). In this way, we avoid repetitive insertion of the same edge intersections, since the companion faces share the same intersection with its neighborhood $f_1$ or $f_2$.

@@

The key observation is that coplanar cases do not create new edges, just like edge intersection in the last section. The difference is that in a non-coplanar case, there is only one edge intersection. In a coplanar, there are at most three intersections. Therefore, we can decompose it into three edge intersections and record each edge intersection independently. However, there is a better way that we do not process them at all. This is because there is companion face, like $T_1^*$, in edge intersection. If $T_1^*$ is not coplanar with $T_2$, then we can solve the intersection between $T_1^*$ and $T_2$ in a 3D way, which is the case in Fig \ref{fig:twin}(c). On the other hand, if $T_1^*$ is coplanar with $T_2$, we instantly know that both sides of shared edge $e(T_1, T_1^*)$ have the same indicator $\boldsymbol{\Lambda}_1$, which imply that this intersection is not necessary for tessellation and we can omit it by the principle of concision. In sum-up, we do not need to handle with coplanar intersection cases.

@@

Using plane-based representation, whether two intersections intersects each other is determined by predicate of orientation of plane against a point. For example, we want determine whether ${\boldsymbol{\Gamma}}_1$ and ${\boldsymbol{\Gamma}}_2$ intersects. Using the notation of section \ref{sec:ir}, we perform the test by checking whether $v_0({\boldsymbol{\Gamma}}_1), v_1({\boldsymbol{\Gamma}}_1)$ are on two sides of $p({\boldsymbol{\Gamma}}_2)$ and whether $v_0({\boldsymbol{\Gamma}}_2), v_1({\boldsymbol{\Gamma}}_2)$ are on two sides of $p({\boldsymbol{\Gamma}}_1)$. If yes, ${\boldsymbol{\Gamma}}_1$ and ${\boldsymbol{\Gamma}}_2$ intersects and introduces new intersection vertex $v_{new}$, which is the intersection of $p({\boldsymbol{\Gamma}}_1), p({\boldsymbol{\Gamma}}_2)$ and the supporting plane of $t({\boldsymbol{\Gamma}}_1)$. The new vertex $v_{new}$ should be added into both ${\boldsymbol{\Gamma}}_1$ and ${\boldsymbol{\Gamma}}_2$ as a segment point. Since there may be more than one segment point added into a certain intersection during the whole test, we do not divide the intersection until all intersection pairs are tested.

@@

The space coherence of indicator vectors means neighboring faces could share the same indicator vector, or most components of indicator vectors. For example, given two neighboring faces $t_1$ and $t_2$, indicator vectors $\boldsymbol{\Lambda}(t_1)$ and $\boldsymbol{\Lambda}(t_2)$ would often be the same. Only when there is boundary of some meshes, say $P_k$, on the shared edge $e(t_1, t_2)$ and split $t_1$ and $t_2$ in two sides, the corresponding components $\boldsymbol{\Lambda}(t_1, P_k)$ and $\boldsymbol{\Lambda}(t_2, P_k)$ can be different. And other components of $\boldsymbol{\Lambda}(t_1)$ and $\boldsymbol{\Lambda}(t_2)$ will remain the same. If we can compute the indicator changes between neighboring faces efficiently, we can start from a single face with a indicator vector as the seed, propagating to all faces with geometry connectivity, reusing indicator vectors according to the spatial coherence and classifying faces very fast.

Fortunately, in the Linked Halfedge, it is straightforward to know whether $\boldsymbol{\Lambda}(t_1, P_k)$ and $\boldsymbol{\Lambda}(t_2, P_k)$ are different, because it means $e(t_1, t_2)$ will be on the boundary of $P_k$, and there will be corresponding I-reps stored on $e(t_1, t_2)$. In addition, both $\boldsymbol{\Lambda}(t_1, P_k)$ and $\boldsymbol{\Lambda}(t_2, P_k)$ can be computed efficiently according to the I-reps (details in Section \ref{sec:individual}). We outline our classification method in Algorithm 1.

@@

\textbf{Output: } Classification of each face $f(\boldsymbol{\Lambda}(t_i)), t_i \in \Omega$

\begin{algorithmic}[1]
\State Select a proper seed face $t_s$
\State Compute the first indicator vector $\boldsymbol{\Lambda}(t_s)$
\State \Call{propagate} { $t_s$ , $\boldsymbol{\Lambda}(t_s)$}
\State
\Function{propagate}{ $t_c$ , $\boldsymbol{\Lambda}(t_c)$}
    \State Compute $f(\boldsymbol{\Lambda}(t_c))$
    \For {each neighboring face $t_i^c$}
        \If {there are I-reps $\{{\boldsymbol{\Gamma}}_k\}$ on $e(t_i^c, t_c)$}
            \State Compute $\boldsymbol{\Lambda}(t_i^c)$ using $\boldsymbol{\Lambda}(t_c)$ and $\{{\boldsymbol{\Gamma}}_k\}$
            \State \Call{propagate} { $t_i^c$ , $\boldsymbol{\Lambda}(t_i^c)$}
        \Else
            \State \Call{propagate} { $t_i^c$ , $\boldsymbol{\Lambda}(t_c)$}
        \EndIf
    \EndFor
\EndFunction
\end{algorithmic}
\end{algorithm}

\subsection{Precise Seed Generation}

@@

However, using point on the boundary instead of an inner one has another problem. Given a face $s$ (may not be triangle) and one of its vertex $v_b^i(s)$, the vertex indicator $\boldsymbol{\Lambda}(v_{i}(s), P_k)$ may cause ambiguity to deduce the face indicator $\boldsymbol{\Lambda}(s, P_k)$. In {\color{red}{Fig. ?}}, $\boldsymbol{\Lambda}(v_b^1(s), P_k) = on$, then $\boldsymbol{\Lambda}(s, P_k)$ can be any of the four conditions. We solve this problem by trying other vertices in $s$ for ambiguous indicators. If all vertices indicators are $on$ and the ambiguity cannot be resolved, the current face is not proper for being the seed and we select a new one instead.

@@

Feito et. al. \cite{feito2013fast} had noticed that intersection neighborhood can be used for fast classification of faces around that intersection. According to their method, faces adjacent to intersection have neighbors from other primitive(s) that define the position and orientation for each other, by which the indicators are determined. However, Feito et. al. did not give detail description of how to implement an exact and robust classification. Their implementation of using vertex coordinates might misclassify faces by numeric errors and fail in degenerate cases. Because geometry connectivity is used, local misclassification can be spread to the neighborhoods, leading to errors in wide ranges.

We develop an classification method that is unconditionally robust and exact based on the idea of using intersection neighborhood information. The neighborhood information is stored in the context component of I-reps during previous stages . In the following, we discuss the conditions that the face to be classified is a triangle. If the face is not a triangle, we select a triangle slice of the face instead, as the whole face is guaranteed to be classified together. Note that the chosen slice should contain the edge where the I-reps lie, by which we compute the new indicators.

Given a face $t_i$ to be classified and an I-rep $\boldsymbol\Gamma$ of intersection on one of $t_i$'s edge, we denote the three corners it as $v_0^{\Gamma}, v_1^{\Gamma}, v_2,$ where the superscript $\boldsymbol\Gamma$ means the vertices are on the edge where $\boldsymbol\Gamma$ lies. We also denote the context component of $\boldsymbol\Gamma$ as $C_{P_h \backslash P_j}$, meaning $t_i$ is from primitive $P_j$ and intersects primitive $P_h$. From previous discussion (section \ref{sec:ir}){\color{red}{may be more than one}}, we know there are two types of intersection context---face neighborhood and edge neighborhood. In both conditions, the one or two faces involving in the context split the space into two in and out space by its (their) orientation(s). We will see that under such division (denoted as $\boldsymbol{D}(C_{P_h \backslash P_j})$), we can compute $\lambda(t_i, P_j)$ exactly.

Since the faces involving in $C_{P_h \backslash P_j}$ is part of primitive $P_j$, the space division $\boldsymbol{D}(C_{P_h \backslash P_j})$ is homogeneous with the space division by $P_j$ in neighborhood of $\boldsymbol{\Gamma}$. The basic idea is to choose one point $v_x$ on $t_i$ close enough to $\boldsymbol{\Gamma}$ to compute $\lambda(v_x, P_j)$, and then compute $\lambda(t_i, P_j)$ accordingly. However, the problem is that we cannot find such a $v_x$ that can be represented exactly, which means robust classification cannot be performed. Fortunately, we observe that we can choose $v_2$, which is not so close to $\boldsymbol{\Gamma}$ instead. To illustrate, assume there is another point $v_{x'}$ in $t_i$ that is very close to $v_2$ ({\color{red}{Fig. x}}). Because all inner points of $t_i$ have the same indicator, $\lambda(v_x, P_j) = \lambda(v_{x'}, P_j)$. On the other hand, we find that $\lambda(v_{x'}, P_j)$ and $\lambda(v_2, P_j)$ are always equal under division $\boldsymbol{D}(C_{P_h \backslash P_j})$ ({\color{red}{may be proved}}). Therefore, $\lambda(v_2, P_j)$ is equal to $\lambda(v_x, P_j)$ under $\boldsymbol{D}(C_{P_h \backslash P_j})$, which is coherent with $\lambda(t_i, P_j)$ under the division of whole primitive $P_j$. One additional thing is that when $\lambda(v_2, P_j)=on$, $\lambda(t_i, P_j)$ can be either $same$ or $oppo$. The orientation test have to be performed to eliminate the ambiguity.

{\color{red}{fen ge xian}}

@@

If $I$ lies on edge of primitive $A$,  the intersection context is face pair: $C_{I \mapsto A} = (f_p^A, f_q^A)$. This situation is a little more complex that we cannot decide $i_A$ until we check the orientations of both $f_p^A$ and $f_q^A$. To correctly classify $f$, we first build BSP structure using $f_p^A$ and $f_q^A$ [?], and then determine the space indicator $i_A(v_2)$ by the BSP. As coordinate of $v_2$ and all the planes can be exactly computed, the classification is exact. The indicator of the face $i_A(f)$ should be the same as $i_A (v_2)$. It is because under a BSP structure with only two division planes, any sample point on $f$ except those on $I$ has the same $\boldsymbol{\Lambda}_A$ (Fig. ??).

@@

If the CSG tree is large, with tens of, or even hundreds of nodes, computing $\boldsymbol{\Lambda}_\Phi(f) = \Phi(\vec{\boldsymbol{\Lambda}}(f))$ for every face can be costly. Considering the space coherence of indicator, we use cache techniques --- by storing the evaluation result of $\Phi$ --- to save the computation time.

The most simple cache strategy is final result cache. We know indicator vector $\vec{\boldsymbol{\Lambda}}$ will not change if there is no intersection context during spreading. That means the final classification $\boldsymbol{\Lambda}_\Phi$ will not change, too. Thus, those faces sharing the same $\boldsymbol{\Lambda}$ can be classified as a whole.

Also, we can also do intermediate result cache. It should be noticed that $\Phi(\vec{\boldsymbol{\Lambda}}(f))$ can be simplified if some components of $\vec{\boldsymbol{\Lambda}}$ is fixed. For example, assume we have a Boolean expression $M_1\cup (M_2\cap M_3-M_4)$. Given the values of two indicators $\boldsymbol{\Lambda}_1(x)=out$, $\boldsymbol{\Lambda}_2(x)=in$, the expression can be rewritten as $out\cup (in\cap M_3-M_4)$. Using the combination rules we can simplify the expression as $M_3-M_4$. This fact is important because for a large CSG tree, a certain primitive, denoted as $M_x$, often only intersects with a few other primitives $\Theta= \{M_{n_1}, M_{n_2}, \cdots, M_{n_k}\}$. That means all the faces in $M_x$ has the same indicators for the primitives not in $\Theta$. Therefore, we can first determine these fixed indicators and simplify the Boolean function $\Phi$ into a simpler one $\Phi_{M_x}$, and then use $\Phi_{M_x}$ to compute the final indicator for each faces.

@@

\vspace{0.5em}
\textbf{Generate Seed Indicator Vector.} Our method of generating the first indicator vector will fail on extreme conditions when all faces in Linked halfedge are coincident with more than one primitive face (e.g., the union of the same mesh). In order to be robust, we use the face barycenter with high-precision coordinates for the point-in-polyhedron test to generate the seed indicator vector after several failures of choosing a proper seed face.
